Feeding Dynamic Behavior into Optimization: Simulation-based Multi-objective Overtime Planning

### 2014-09-01 data/result/Article/Latex/Article.tex
Ajustes no LaTeX

\documentclass[conference]{IEEEtran}
\usepackage{graphicx}
\usepackage{array}
\usepackage{bigstrut}
\usepackage{rotating}
\usepackage{multirow}
\usepackage{booktabs}
\hyphenation{op-tical net-works semi-conduc-tor}

@@

\noindent
\textbf{RQ1 (Validation):} How does NSGAII perform if compared to random search on finding solutions for OPP? This is a "sanity check" to determine if our formulation allows a systematic search to outperform random search. If such cannot be verified, either the formulation is poorly designed, parameters are not adequate, or the problem is simple enough to allow a non-systematic procedure to find good solution.

@@

\noindent
\textbf{RQ1:} To compare NSGAII to random search (RS), we ran 50 independent optimization cycles for both algorithms using the same stop criteria. NSGAII achieved higher I$_{HV}$, higher I$_{C}$, and lower I$_{GD}$ on all instances compared to RS. Wilcoxon-Mann-Whitney tests applied on an instance basis found significant differences between results produced by the algorithms at 95\% significance level for all quality indicators and all instances. Standardized effect-sizes (non-parametric Vargha-Delaney {\^A}12 test) also indicate that NSGAII produces higher I$_{HV}$ and lower I$_{GD}$ in 100\% of the runs, while producing higher I$_{C}$ for more than 88\% of these runs. Thus, there is strong evidence that NSGAII outperforms RS while searching for solutions for the OPP and that our formulation and parametrization pass the "sanity check" implied in RQ1.

\noindent
\textbf{RQ2:} To address this question we compared our formulation for the OPP with three overtime management strategies (OMS) presented by Ferrucci et al. \cite{Ferrucci:2013} as reference practices from the industry: (i) ''margarine'' management (MAR) suggests spreading overtime hours evenly over all activities comprising the schedule; (ii) Critical Path (CPM) suggests loading overtime onto the schedule's critical path to reduce completion time and risk of schedule overrun; and (iii) Second Half (SH) suggests loading overtime onto the later part of the schedule to compensate for delays introduced in early activities.

@@

On regard on I$_{C}$, SH contributed with more vertices to the reference Pareto front than the average front produced by each cycle of NSGAII in 4 out of 6 instances. For the remaining instances, results slightly favor NSGAII, but without statistical significance in comparison with SH. On average, SH contributed with 5.2 solutions to the reference front, while NSGA-II contributed with 2.4 solutions. Each remaining OMS contributed with a single solution to the front (zero overtime). On regard of I$_{HV}$, NSGAII produced the best results except for the largest instance (PARM), on which it was significantly outperformed by SH. Finally, on regard of I$_{GD}$ NSGAII outperformed all OMS in 4 out of 6 instances, losing to SH on the OMET and PARM instances (the largest instances). For the latter, all solutions produced by SH were part of the reference front. Thus, we ratify the results presented by Ferrucci et al. \cite{Ferrucci:2013} in the sense that the CPM and margarine OMS are not competitive with optimization results. On the other hand, SH seems competitive and outperforms NSGAII in terms of closeness to the reference front on large instances.

@@

% Table generated by Excel2LaTeX from sheet 'tabela 6'
\begin{table}[htbp]
	\scriptsize
  \centering
  \caption{Average difference in makespan and cost for solutions involving excessive overtime for each instance. data shows that the formulation without overtime error dynamics tends to understimate both cost and makespan for most projects.}
    \begin{tabular}{rccc}
    \toprule
    \multicolumn{1}{c}{\multirow{2}[2]{*}{\textbf{Instance}}} & \multirow{2}[2]{*}{\textbf{Overtime  Range}} & \multicolumn{2}{c}{\textbf{(NSGA$_{NE}>$NSGA-II)}} \\

@@

\begin{figure*}
\centering
\includegraphics[scale=0.65]{2dplots.pdf}
\caption{2D projections for combinations of the number of overtime hours, makespan, and cost objectives for the smaller (ACAD) and largest (PARM) instances. The linear relations resulting from NSGA$_{NE}$ and the convex shape of NSGA-II can be observed, as well as the few solutions provided by each OMS.}
\end{figure*}

@@

Knee-points connecting different regions of the Pareto front (such as the one described above) can be explored by decision-makers as overtime allocation alternatives on which large changes in one objective can be garnered by accepting small compromises on other objectives. This allows decision-makers to answer questions such as "what must I do to reduce makespan?", "how much does it cost to reduce makespan by X days?" or "which activities provide the best leverage for a certain amount of overtime?".

@@

We observed that our approach performs significantly better (high effect-size) than the margarine and critical-path overtime-allocation strategies. However, the practice that suggests allocating overtime in the second half of the project's schedule is competitive with our approach and may lead to good overtime allocations, specially in large projects. This behavior confirms the "gut-feeling" of practitioners who tend to allocate overtime in the last activities to compensate for earlier delays. Therefore, by combining search-based optimization and software project simulation we can help researchers to design experimental studies to investigate, evaluate, and provide scientific support for practices and assumptions used in the industry, converting intuition into evidence-based knowledge.

>>>>

\documentclass[conference]{IEEEtran}
\usepackage{graphicx}
\usepackage{array}
\usepackage{bigstrut}
\usepackage{rotating}
\usepackage{multirow}
\usepackage{booktabs}
\hyphenpenalty=10000

@@

\noindent
\textbf{RQ1 (Validation):} How does NSGAII perform if compared to random search on finding solutions for OPP? This is a ``sanity check" to determine if our formulation allows a systematic search to outperform random search. If such cannot be verified, either the formulation is poorly designed, parameters are not adequate, or the problem is simple enough to allow a non-systematic procedure to find good solution.

@@

\noindent
\textbf{RQ1:} To compare NSGAII to random search (RS), we ran 50 independent optimization cycles for both algorithms using the same stop criteria. NSGAII achieved higher I$_{HV}$, higher I$_{C}$, and lower I$_{GD}$ on all instances compared to RS. Wilcoxon-Mann-Whitney tests applied on an instance basis found significant differences between results produced by the algorithms at 95\% significance level for all quality indicators and all instances. Standardized effect-sizes (non-parametric Vargha-Delaney {\^A}12 test) also indicate that NSGAII produces higher I$_{HV}$ and lower I$_{GD}$ in 100\% of the runs, while producing higher I$_{C}$ for more than 88\% of these runs. Thus, there is strong evidence that NSGAII outperforms RS while searching for solutions for the OPP and that our formulation and parametrization pass the ``sanity check" implied in RQ1.

\noindent
\textbf{RQ2:} To address this question we compared our formulation for the OPP with three overtime management strategies (OMS) presented by Ferrucci et al. \cite{Ferrucci:2013} as reference practices from the industry: (i) ``margarine" management (MAR) suggests spreading overtime hours evenly over all activities comprising the schedule; (ii) Critical Path (CPM) suggests loading overtime onto the schedule's critical path to reduce completion time and risk of schedule overrun; and (iii) Second Half (SH) suggests loading overtime onto the later part of the schedule to compensate for delays introduced in early activities.

@@

On regard on I$_{C}$, SH contributed with more vertices to the reference Pareto front than the average front produced by each cycle of NSGAII in 4 out of 6 instances. For the remaining instances, results slightly favor NSGAII, but without statistical significance in comparison with SH. On average, SH contributed with 5.2 solutions to the reference front, while NSGAII contributed with 2.4 solutions. Each remaining OMS contributed with a single solution to the front (zero overtime). On regard of I$_{HV}$, NSGAII produced the best results except for the largest instance (PARM), on which it was significantly outperformed by SH. Finally, on regard of I$_{GD}$ NSGAII outperformed all OMS in 4 out of 6 instances, losing to SH on the OMET and PARM instances (the largest instances). For the latter, all solutions produced by SH were part of the reference front. Thus, we ratify the results presented by Ferrucci et al. \cite{Ferrucci:2013} in the sense that the CPM and margarine OMS are not competitive with optimization results. On the other hand, SH seems competitive and outperforms NSGAII in terms of closeness to the reference front on large instances.

@@

% Table generated by Excel2LaTeX from sheet 'tabela 6'
\begin{table}[htbp]
	\scriptsize
  \centering
  \caption{Average difference in makespan and cost for solutions involving excessive overtime for each instance. data shows that the formulation without overtime error dynamics tends to understimate both cost and makespan for most projects.}
    \begin{tabular}{rccc}
    \toprule
    \multicolumn{1}{c}{\multirow{2}[2]{*}{\textbf{Instance}}} & \multirow{2}[2]{*}{\textbf{Overtime  Range}} & \multicolumn{2}{c}{\textbf{(NSGA$_{NE}>$NSGAII)}} \\

@@

\begin{figure*}
\centering
\includegraphics[scale=0.65]{2dplots.pdf}
\caption{2D projections for combinations of the number of overtime hours, makespan, and cost objectives for the smaller (ACAD) and largest (PARM) instances. The linear relations resulting from NSGA$_{NE}$ and the convex shape of NSGAII can be observed, as well as the few solutions provided by each OMS.}
\end{figure*}

@@

Knee-points connecting different regions of the Pareto front (such as the one described above) can be explored by decision-makers as overtime allocation alternatives on which large changes in one objective can be garnered by accepting small compromises on other objectives. This allows decision-makers to answer questions such as ``what must I do to reduce makespan?", ``how much does it cost to reduce makespan by X days?" or ``which activities provide the best leverage for a certain amount of overtime?".

@@

We observed that our approach performs significantly better (high effect-size) than the margarine and critical-path overtime-allocation strategies. However, the practice that suggests allocating overtime in the second half of the project's schedule is competitive with our approach and may lead to good overtime allocations, specially in large projects. This behavior confirms the ``gut-feeling" of practitioners who tend to allocate overtime in the last activities to compensate for earlier delays. Therefore, by combining search-based optimization and software project simulation we can help researchers to design experimental studies to investigate, evaluate, and provide scientific support for practices and assumptions used in the industry, converting intuition into evidence-based knowledge.
